---
# PLEASE SEE THE README for in depth description github.com/brentthorne/posterdown
poster_height: "48in"
poster_width: "36in"
font_family: 'Rasa'
#ESSENTIALS
title: '**Feature Extraction with fxtract**'
author:
  - name: '**Quay Au**'
    affil: 1
    main: true
    orcid: '0000-0002-5252-8902'
    email: quay.au@stat.uni-muenchen.de
  - name: Clemens Stachl
    affil: 2
  - name: Ramona Schoedel
    affil: 2
  - name: Theresa Ullmann
    affil: 1
  - name: Andreas Hofheinz
    affil: 1
  - name: Bernd Bischl
    affil: 1
affiliation:
  - num: 1
    address: Institute of Statistics, Ludwigs-Maximilians-University München
  - num: 2
    address: Department of Psychology, Methods and Assessment, Ludwigs-Maximilians-University München
#STYLE & FORMATTING
title_textsize: "125pt"
author_textsize: "1.17em"
authorextra_textsize: "35px"
affiliation_textsize: "25px"
affiliation_textcol: '#00000080'
caption_fontsize: "20pt"
#Middle of the poster
middle_fontfamily: "Rasa"
middle_textcol: "#FFFFFF"
middle:textalpha: 90
middle_fontsize: "170px"
main_findings:
  - "Feature Extraction with **fxtract**"
  - "An R-Package for Extracting **User-defined** Features from Grouped Data"
logoleft_name: "../man/figures/hexagon.svg"
logocenter_name: "Figures/qr-code-black.png"
logoright_name: "../man/figures/hexagon.svg"
#---POSTER BODY OPTIONS---#
primary_colour: '#7D0000'
secondary_colour: "#150001"
accent_colour: "#cc0000"
body_bgcol: "#ffffff"
body_textsize: "45px"
body_textcol: "#000000"
reference_textsize: "23px"
#--Standard Options--#
output: 
  posterdown::posterdown_betterport:
    self_contained: false
    pandoc_args: --mathjax
    highlight: espresso
    number_sections: true
bibliography: MyBib.bib
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(
  results = 'asis',
  echo = FALSE,
  comment = FALSE,
  warning = FALSE,
  message = FALSE,
  fig.align = 'center'
)
```

# Introduction

Feature extraction is a crucial step for tackling machine learning problems. Many machine learning problems start with complex (often timestamped) raw data with many grouped variables (e.g. heart rate measurements of many patients, gps data for analysis of movements of many participants of a study, etc.). Often times, this raw data cannot directly be used for machine learning algorithms. User-defined features must be extracted for this purpose. Examples could be the heart rate variability of a patient, or the maximum distance traveled by a participant of a gps study. Since there are many different machine learning applications and therefore many inherently different raw datasets and features which need to be calculated, we do not supply any automated features. fxtract assists you in the feature extraction process by helping with the data wrangling needed, but still allows you to extract your own defined features.

```{r pressure, echo=FALSE, fig.cap="A caption", out.width = '100%'}
knitr::include_graphics("../man/figures/fxtract_main.svg")
```

# Usage

## Design Principles

## Error Handling

## Parallelization

