---
title: "R6 Class Project - How to Update a Feature"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{fxtract}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

Use case:

- Features have been added (or have already been calculated).
- We want to edit a feature function.

```{r test-main, child = 'project_setup_child.Rmd', message = FALSE}
```

All features have been calculated:
```{r, message = FALSE}
my_project$results
```

## Write Updated Feature Functions
Let's say we want to edit our features to use the robust measures `median()` and `mad()`.

First we need to write the functions:
```{r, message = FALSE}
fun1_robust = function(data) {
  c(median_sepal_length = median(data$Sepal.Length),
    mad_sepal_length = mad(data$Sepal.Length))
}

fun2_robust = function(data) {
  c(median_petal_length = median(data$Petal.Length),
    mad_petal_length = mad(data$Petal.Length))
}
```

## Delete Old Feature Functions
```{r, message = FALSE}
my_project$remove_feature(fun1)
```
This deletes all calculated features corresponding to `fun1`.

It's also possible to pass a character string:
```{r, message = FALSE}
my_project$remove_feature("fun2")
```

## Add New Feature Functions
All there is left to do is to add the new feature functions and to execute the calculation process:

```{r, message = FALSE}
my_project$add_feature(fun1_robust)
my_project$add_feature(fun2_robust)
```
```{r, message = FALSE}
my_project$calc_features()
my_project$results
```

```{r, echo = FALSE}
unlink("projects", recursive = TRUE)
```
