---
title: "Frequently Asked Questions"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{fxtract}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

### My R session crashed. Can I continue extracting features or do I have to start from the beginning?

### How can I parallelize calculation? What is parallelized? 

### How do I handle exported objects and packages for parallelization?
Thanks to the [`future`](https://cran.r-project.org/web/packages/future/vignettes/future-1-overview.html) package, global variables and functions are automatically identified and exported as needed.
Make sure to have these variables and functions in your global environment, especially after loading an xtractor.

### How can I monitor the progress of calculation?

### What happens behind the scenes?

### Where are the files saved?
The default file directory is your current working directory. Files are saved in the newly created folder *fxtract_files/YOUR_XTRACTORS_NAME*.

### My feature function is stochastical. Does your package handle seeding?

```{r}
unlink("fxtract_files", recursive = TRUE)
```

```{r, results = "hide"}
library(fxtract)
set.seed(1)
x = Xtractor$new("x")
x$add_data(data.frame(ID = as.character(1:10)), group_by = "ID")
fun = function(data) c(random_number = rnorm(1))
x$add_feature(fun)
x$n_cores = 4
x$calc_features()
```

```{r, results = "hide"}
set.seed(1)
y = Xtractor$new("y")
y$add_data(data.frame(ID = 1:10), group_by = "ID")
fun = function(data) c(random_number = rnorm(1))
y$add_feature(fun)
y$n_cores = 4
y$calc_features()
```
```{r}
all.equal(x$results, y$results)
```


### What are pros and contras of your package?

### How large can my dataset be?