---
title: "Filters"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{fxtract}
  \usepackage[utf8]{inputenc}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---
<!-- write something about why it's useful to use our filters -->
We included some preprocessing functions which help filtering a dataset by time and weekday.
This is especially useful for analyzing behavioral data, since human behavior tends to differ between weekday and weekends and also between different times.

# filter_daytime
You can filter your dataset by time. You will get every day with times inside the interval:
```{r, eval = FALSE}
df = add_time(studentlife_small, utc_col = "timestamp")
filter_daytime(df, from_time = "06:00:00", until_time = "09:00:00")
```

# filter_weekday
You can filter your dataset by a given timeframe (e.g. from Monday 6am to Friday 6pm):
```{r, eval = FALSE}
df = add_time(studentlife_small, utc_col = "timestamp")
df = add_weekday(df, utc_col = "timestamp")
filter_weekday(df, from_day = "Mon", from_time = "06:00:00", until_day = "Fri", until_time = "18:00:00")
```

