---
title: "Add Date Information"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{fxtract}
  \usepackage[utf8]{inputenc}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---
We included some handy timestamp converters which enrich datasets with useful information.
Let's demonstrate it with a simple example:
```{r, message = FALSE}
library(fxtract)
df = data.frame(timestamp = c(946733820, 946733821, 946733822), x = "some_data")
#corresponds to 2000-01-01 13:37, 2000-01-01 13:37:01, 2000-01-01 13:37:02
df
```


## add_date_time
This function adds a date_time variable from the [lubridate](https://www.rdocumentation.org/packages/lubridate/versions/1.7.4/topics/as_date) package to your dataset:
```{r}
add_date_time(data = df, utc_col = "timestamp")
```


## add_date
This function adds a date variable from the [lubridate](https://www.rdocumentation.org/packages/lubridate/versions/1.7.4/topics/as_date) package to your dataset:

```{r}
add_date(data = df, utc_col = "timestamp")
```


## add_weekday
This funciton adds an ordered weekday variable from the [lubridate](https://www.rdocumentation.org/packages/lubridate/versions/1.7.4/topics/day) package to your dataset:
```{r, message = FALSE, warning = FALSE}
add_weekday(data = df, utc_col = "timestamp")
```

## add_time
This funciton adds a time variable [lubridate](https://www.rdocumentation.org/packages/lubridate/versions/1.7.4/topics/as_date) package to your dataset:
```{r}
add_time(data = df, utc_col = "timestamp")
```
