---
title: "Use Cases"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{fxtract}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

# Introduction
To demonstrate the functionalities of the fxtract package we use the studentlife data set.
The data set can be downloaded [here](http://studentlife.cs.dartmouth.edu/dataset.html)

Safe studentlife data files into studentlife/dataset folder

Goals:
- Save studentlife data in SQL database 
- create features from loggingdata directly from a SQL database, because data is too big for RAM.
- Show a few timestamp helper functions

```{r, eval = FALSE, warning=FALSE, echo = FALSE}
library(dplyr)
library(stringr)
library(devtools)
load_all()

con = src_sqlite("studentlife/SQL_database.sql", create = TRUE)

# Ingestion of Appusage data
lsFiles = list.files(path="studentlife/dataset/app_usage", full.names=TRUE, recursive=FALSE)
lsData = lapply(lsFiles, function(x) {
    df_temp = read.csv(x, header=TRUE, fileEncoding="UTF-8-BOM") # load file
    userId = str_sub(x,  -7, -5)
    df_temp$userId = userId
    df_temp$source = "app"
    df_temp
})

# Create data frame with app data
app = do.call(bind_rows, lsData)

# Calls data
lsFiles = list.files(path="studentlife/dataset/call_log", full.names=TRUE, recursive=FALSE)
lsData = lapply(lsFiles, function(x) {
    df_temp = read.csv(x, header=TRUE, fileEncoding="UTF-8-BOM") # load file
    userId = str_sub(x,  -7, -5)
    df_temp$userId = userId
    df_temp$source = "calls"
    df_temp
})

# Create data frame with calls data
calls = do.call(bind_rows, lsData)

# GPS data
lsFiles = list.files(path="studentlife/dataset/sensing/gps", full.names=TRUE, recursive=FALSE)
lsData = lapply(lsFiles, function(x) {
    df_temp = read.csv(x, header=TRUE, fileEncoding="UTF-8-BOM") # load file
    userId = str_sub(x,  -7, -5)
    df_temp$userId = userId
    df_temp$source = "gps"
    df_temp
})

# Create data frame with gps data
gps = do.call(bind_rows, lsData)

# Combine data frames and save as data base
data_all = app %>% bind_rows(calls) %>% bind_rows(gps) %>% addDate(utc_col = "timestamp")

# Write data to data base
copy_to(con, data_all, name = "studentlife_data", temporary = F, overwrite = T)


```

## Load data of first user
```{r}
data = tbl(con, "studentlife_data") %>% select(everything()) %>% filter(userId == "u00")
df = as.data.frame(data)
```

# Features
## Number different apps
```{r}
featureNumDiffApps = function(data) length(unique(data$RUNNING_TASKS_baseActivity_mPackage))

nApps = featureNumDiffApps(df)
print(paste("Number of different apps:", nApps))
```

## Mean Number different apps per day
```{r}
featureMeanNumDiffAppsPerDay = function(data) {
  n = data %>% dplyr::group_by(date) %>% distinct(RUNNING_TASKS_baseActivity_mPackage) %>% summarize(n = n()) %>% pull(n)
  return(data.frame(mean = mean(n), sd = sd(n)))
}

nMeanDiffApps = featureMeanNumDiffAppsPerDay(df)
print(paste("Mean number of different apps per day", round(nMeanDiffApps[1],2), "with standard deviation", round(nMeanDiffApps[2],2)))
```

## gps - maximum distance
```{r, echo = FALSe}
library(geosphere)

gpsAvailable = df %>% filter(!is.na(latitude), !is.na(longitude), latitude >= 0, latitude <= 360, longitude >= 0, longitude <= 360)

maxDistKm = function(data) max(distm(cbind(gpsAvailable$longitude,gpsAvailable$latitude))) / 1000

maxDistKm = maxDistKm(data)
print(paste("Maximum distance:", round(maxDistKm,2), "km"))

```

## calls - total number calls
```{r}
totalCalls = function(data) data %>% filter(!is.na(CALLS__id)) %>% summarize(nCalls = n())
nCalls = totalCalls(df)
print(paste("Number of total calls:", nCalls))
```


# show shiny app


















