---
title: "R6 Class Xtractor"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{fxtract}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r, echo = FALSE}
unlink("fxtract_files", recursive = TRUE)
```

- Designed for large projects.
- Data and features can be updated easily.
- Data can be preprocessed.
- Features are calculated on each ID of a grouping variable individually.
- Easy parallelization with `future`.
- Scales nicely for larger datasets. Data is only read into RAM, when needed.

```{r, message = FALSE}
library(fxtract)
xtractor = Xtractor$new("xtractor")
```

## Add Data
Data must be added as dataframes with `$add_data`, where the grouping variable must be specified.
You can also add dataframes for each ID individually. This is especially helpful for large datasets.

- Add all data at once:
```{r, message = FALSE, warning = FALSE}
xtractor$add_data(iris, group_by = "Species")
```

- Add datasets individually:
```{r, message = FALSE, warning = FALSE}
library(dplyr)
for (i in unique(iris$Species)) {
  iris_i = iris %>% filter(Species == i)
  xtractor$add_data(iris_i, group_by = "Species")
}  
```


## Add Features
Features must be added as functions which have a dataframe as input and a named vector as output.
A named list with atomic entries of length 1 is also allowed as output (useful for numerical and categorical outputs).
This function will be calculated for each ID of a grouping variable individually.
```{r, message = FALSE}
fun1 = function(data) {
  c(mean_sepal_length = mean(data$Sepal.Length),
    sd_sepal_length = sd(data$Sepal.Length))
}

fun2 = function(data) {
  list(mean_petal_length = mean(data$Petal.Length),
    sd_petal_length = sd(data$Petal.Length))
}
```


```{r, message = FALSE}
xtractor$add_feature(fun1)
xtractor$add_feature(fun2)
```

## Calculate Features
Features are calculated by the method `$calc_features()`:
```{r, message = FALSE}
xtractor$calc_features()
```

## Collect Results
The desired final dataframe can be accessed by the slot `$results`:
```{r, message = FALSE}
xtractor$results
```

```{r, echo = FALSE}
unlink("fxtract_files", recursive = TRUE)
```
