---
title: "R6 Class Xtractor - Error Handling"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{fxtract}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

Use case:

- When some features fail on some datasets, we can get individual error messages and fix the problem.

Setup script:

```{r, echo = FALSE}
unlink("fxtract_files", recursive = TRUE)
```
```{r, message = FALSE, warning = FALSE, results = "hide"}
library(fxtract)
xtractor = Xtractor$new("xtractor")
xtractor$add_data(iris, group_by = "Species")
```

Let's write functions, which fail on different datasets:

```{r, message = FALSE}
fun1 = function(data) {
  if ("versicolor" %in% data$Species) stop("fun1 not compatible on versicolor")
  c(mean_sepal_length = mean(data$Sepal.Length),
    sd_sepal_length = sd(data$Sepal.Length))
}

fun2 = function(data) {
  if ("virginica" %in% data$Species) stop("fun2 not compatible on virginica")
  c(mean_petal_length = mean(data$Petal.Length),
    sd_petal_length = sd(data$Petal.Length))
}

xtractor$add_feature(fun1)
xtractor$add_feature(fun2)
xtractor$calc_features()
```

We can still get the resulting dataframe with missing values for failed calculations:
```{r}
xtractor$results
```

## Get Error Messages

```{r, message = FALSE, warning = FALSE}
xtractor$error_messages
```

## Debugging
You can get the feature function and the dataset of the ID like this:

```{r, message = TRUE}
fun = xtractor$get_feature("fun1")
df = xtractor$get_data("versicolor")
```
Now you can debug the function on the dataset on which the function failed.

## Fix Features 
```{r, message = FALSE}
fun1_fixed = function(data) {
  c(mean_sepal_length = mean(data$Sepal.Length),
    sd_sepal_length = sd(data$Sepal.Length))
}

fun2_fixed = function(data) {
  c(mean_petal_length = mean(data$Petal.Length),
    sd_petal_length = sd(data$Petal.Length))
}

xtractor$remove_feature(fun1)
xtractor$remove_feature(fun2)
xtractor$add_feature(fun1_fixed)
xtractor$add_feature(fun2_fixed)
```


## Calculate Again
```{r, message = FALSE}
xtractor$calc_features()
xtractor$results
```

```{r, echo = FALSE}
unlink("fxtract_files", recursive = TRUE)
```
